Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-25 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
FDS Flame height ref and values
update tex file

\begin{table}[t!]
  \centering
  \begin{tabular}{l|l}
  	Abbreviations \\
     \hline
     HRR	            & heat release rate (kW) \\
     NIST        	    & National Institute of Standards and Technology (US) \\
     PUF                & polyurethane foam  \\
     $\dot{q}''$        & heat flux per unit area kW/m$^2$ \\
	 $\dot{Q}$          & heat release rate (kW) \\ 
	 $\chi_r$           & radiative fraction \\
	 $R$                & distance from the point source to the target (m) \\
   \end{tabular}
 \end{table}

@@

Computational grid cell sizes of 80~mm, 40~mm, and 20~mm where used in FDS to model the fire.  The resulting plume resolutions were approximately 4.4, 8.8, and 17.5 respectively. Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.  Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the data from

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
		\hline 0.8			   & 442						& 600					& 522			& 198	\\
		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.61~m from the Wall]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume2d}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 604					& 658 			& 667 	\\
		\hline 0.4			   & 751					   	& 824					& 793			& 643 	\\
		\hline 0.6			   & 668						& 711					& 673			& 577 	\\
		\hline 0.8			   & 519						& 575					& 581			& 353	\\
		\hline 1.0			   & 431						& 475 					& 506			& 357	\\
		\hline 1.2			   & 326						& 357 					& 406			& 306	\\
		\hline 1.4			   & 274						& 285 					& 322			& 233	\\
		\hline 1.6			   & 218						& 234 					& 257			& 201	\\
		\hline 1.8			   & 191						& 198 					& 211			& 179	\\
		\hline 2.0			   & 162						& 170 					& 178			& 150	\\
		\hline 2.2			   & 146						& 148 					& 153			& 140	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.0~m from the Wall.]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.0~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume0d}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 207					   & 367					& 316 			 	\\
		\hline 0.4			   & 518					   & 415					& 388			 	\\
		\hline 0.6			   & 487					   & 445					& 434			 	\\
		\hline 0.8			   & 368					   & 393					& 401				\\
		\hline 1.0			   & 284					   & 326 					& 338				\\
		\hline 1.2			   & 189					   & 226 					& 247				\\
		\hline 1.4			   & 150					   & 167 					& 177				\\
		\hline 1.6			   & 113					   & 126 					& 127				\\
		\hline 1.8			   & 97						   & 100 					& 96				\\
		\hline 2.0			   & 81						   & 82 					& 77				\\
		\hline 2.2			   & 72						   & 71 					& 66				\\
		\hline
	\end{tabular}
	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m}
	\label{tab:FDSRI_wall0D}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 219					   & 182					& 158 			 	\\
		\hline 0.4			   & 310					   & 232					& 217			 	\\
		\hline 0.6			   & 272					   & 231					& 250			 	\\
		\hline 0.8			   & 192					   & 189					& 241				\\
		\hline 1.0			   & 152					   & 149 					& 204				\\
		\hline 1.2			   & 113					   & 104 					& 150				\\
		\hline 1.4			   & 96						   & 82 					& 111				\\
		\hline 1.6			   & 79						   & 69 					& 87				\\
		\hline 1.8			   & 70						   & 61 					& 72				\\
		\hline 2.0			   & 60						   & 55 					& 64				\\
		\hline 2.2			   & 51						   & 52 					& 58				\\
		\hline
	\end{tabular}
	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m}
	\label{tab:FDSRI_wallp5D}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 143					   & 132					& 109 			 	\\
		\hline 0.4			   & 180					   & 165					& 142			 	\\
		\hline 0.6			   & 158					   & 165					& 161			 	\\
		\hline 0.8			   & 114					   & 139					& 157				\\
		\hline 1.0			   & 90						   & 111 					& 136				\\
		\hline 1.2			   & 66						   & 76 					& 100				\\
		\hline 1.4			   & 57						   & 59 					& 74				\\
		\hline 1.6			   & 48						   & 49 					& 58				\\
		\hline 1.8			   & 44						   & 44 					& 50				\\
		\hline 2.0			   & 40						   & 42 					& 47				\\
		\hline 2.2			   & 38						   & 41 					& 45				\\
		\hline
	\end{tabular}
	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m}
	\label{tab:FDSRI_wall1D}
\end{table}

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 88						   & 69						& 59 			 	\\
		\hline 0.4			   & 103					   & 82						& 74			 	\\
		\hline 0.6			   & 95						   & 81						& 78			 	\\
		\hline 0.8			   & 76						   & 74						& 76				\\
		\hline 1.0			   & 64						   & 64 					& 67				\\
		\hline 1.2			   & 50						   & 51 					& 55				\\
		\hline 1.4			   & 43						   & 42 					& 45				\\
		\hline 1.6			   & 36						   & 35 					& 37				\\
		\hline 1.8			   & 32						   & 30 					& 31				\\
		\hline 2.0			   & 28						   & 27 					& 28				\\
		\hline 2.2			   & 26						   & 25 					& 26				\\
		\hline
	\end{tabular}
	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m}
	\label{tab:FDSRI_wall2D}
\end{table}

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
		\hline 0.8			   & 442						& 600					& 522			& 198	\\
		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
		\hline
	\end{tabular}
	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
	\label{tab:FDSRI_Exp_Plume}
\end{table}

@@

Table to compare measured flame height with FDS cal.

@@

@@

\bibliography{../References/Madrzykowski_Thesis}
\end{document}

>>>>

\clearpage
Abbreviations
\begin{tabbing}
\hspace{1.5in} \= \\
EMS \> Emergency Medical Services \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

List of Symbols
\begin{tabbing}
\hspace{1.5in} \= \\
$c_{p}$ \> specific heat \\
$k$ \> thermal conductivity \\
$\chi_r$ \> radiative fraction \\
$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
$\dot{Q}$ \> heat release rate (kW) \\ 
$R$ \> distance from the point source to the target (m) \\
$\rho$ \> density \\
\end{tabbing}

@@

Computational grid cell sizes of 80~mm, 40~mm, and 20~mm where used in FDS to model the fire.  The resulting plume resolutions were approximately 4.4, 8.8, and 17.5 respectively. Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices. Tables~\ref{tab:FDSRI_Exp_Plume2d} and \ref{tab:FDSRI_Exp_Plume0d} shows the plume temperature results for the three grid resolutions compared the experimental data with a wall spacing of 0.61~m and 0.0~m respectively. Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the same data.

\begin{table}[ht!]
  \small
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid    & Experiment Avg. \\
    Burner~(m)     & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C) \\ \hline
    \hline 0.2         & 458            & 500           & 666     & 620   \\
    \hline 0.4         & 738            & 819           & 761     & 527   \\
    \hline 0.6         & 632            & 769           & 643     & 385   \\
    \hline 0.8         & 442            & 600           & 522     & 198 \\
    \hline 1.0         & 346            & 459           & 402     & 151 \\
    \hline 1.2         & 251            & 307           & 284     & 119 \\
    \hline 1.4         & 209            & 236           & 213     & 98  \\
    \hline 1.6         & 166            & 188           & 164     & 86  \\
    \hline 1.8         & 145            & 154           & 133     & 76  \\
    \hline 2.0         & 123            & 130           & 112     & 69  \\
    \hline 2.2         & 111            & 113           & 99      & 61  \\
    \hline
  \end{tabular}
  \caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.61~m from the Wall]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
  \label{tab:FDSRI_Exp_Plume2d}
\end{table}

\begin{table}[ht!]
  \small
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid    & Experiment Avg. \\
    Burner~(m)     & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C) \\ \hline
    \hline 0.2         & 458            & 604           & 658     & 667   \\
    \hline 0.4         & 751            & 824           & 793     & 643   \\
    \hline 0.6         & 668            & 711           & 673     & 577   \\
    \hline 0.8         & 519            & 575           & 581     & 353 \\
    \hline 1.0         & 431            & 475           & 506     & 357 \\
    \hline 1.2         & 326            & 357           & 406     & 306 \\
    \hline 1.4         & 274            & 285           & 322     & 233 \\
    \hline 1.6         & 218            & 234           & 257     & 201 \\
    \hline 1.8         & 191            & 198           & 211     & 179 \\
    \hline 2.0         & 162            & 170           & 178     & 150 \\
    \hline 2.2         & 146            & 148           & 153     & 140 \\
    \hline
  \end{tabular}
  \caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.0~m from the Wall.]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.0~m from the Wall.}
  \label{tab:FDSRI_Exp_Plume0d}
\end{table}

@@

@@

@@

Table to compare measured flame height with FDS cal~\cite{McDermott:2011}

Flame Height 2D  20~mm  at 99~\%  1.28~m

Flame Height 0D  20~mm  at 99~\%  1.46~m

@@

lessons learned  cameras   black paint

@@

\bibliography{../References/Madrzykowski_Thesis}

\end{document}
